Outline of Ideas for BTC Transaction Frequency

### 2015-10-13 outline/outline.tex
Better explanation of why I think strategic behavior is happening

These estimates seem rather high considering no block have filled up yet. Transaction rates have been fluctuating around 0.05 for several months and even under constant transaction rates, the probability of a full block over 0.1. This may be explained by several things. First, possibly transaction rates are usually low and only occasionally spike so that only during a spike is there a real chance of a block filling up. Another possibility is that Bitcoin traders are cognizant of the size limit and when a block is near full they wait to make their trades until a new block arrives. Since they would only have to wait 10 minutes to complete their transaction, on average, waiting it not much of a nuisance so the costs are small.

>>>>

These estimates seem rather high considering no block have filled up yet. Transaction rates have been fluctuating around 0.05 for several months and even under constant transaction rates, the probability of a full block is over 0.1. Even at a constant transaction rate of 0.02, the probability of a full block is 0.067. In 100 blocks, which is approximately 17 hours, the probability of at least one block filling up is $1-(1-0.067)^{100}\approx 1$. Since no block has filled up yet, clearly something is happening that prevents blocks from filling up. One possibility is that transaction rates are usually low and in no danger of causing a full block, but occasionally there are large spikes in the rate. Another possibility is strategic action by Bitcoin traders and miners to prevent blocks from filling up. Traders may be waiting to trade until a new block replaces a nearly full block, which is not much of a cost since the wait is only about 10 minutes on average. Similarly miners have an incentive to keep blocks small since that reduces the change of an orphan block --- a mined block which is not accepted by the blockchain --- so the miner of the current block may be rejecting some transactions in order to prevent the limit from being reached.
